Ultrafast Electron Microscopes: Design Criteria, Electron Sources, and Column Modeling

### 2013-04-03 inc/hardware/introduction.tex
merge andreas' comments on hardware introduction

It is common in the DTEM field to modify an existing Transmission Electron Microscope column, adapting it for laser-stimulated electron generation.
For the reasons covered in Section \ref{sec:childs_law}, the prototype UEM at UIC is being built to accomodate large width electron pulses.
To satisfy this restriction, it has been designed and built from parts either fabricated in-house or from commercially available, both for the ease of prototyping inherent in using replacable parts and the accomodate the physical limitations our choice of a large beam width have imposed on the standard electron microscope column components.

>>>>

It is common in the DTEM field to modify an existing transmission electron microscope column, adapting it for laser-stimulated electron generation.
For the reasons covered in Section \ref{sec:childs_law}, the prototype UEM at UIC is being built to accomodate electron pulses with a large transverse size.
To satisfy this restriction, it has been designed and built from parts either fabricated in-house or from commercially available sources, both for the ease of prototyping inherent in using replacable parts and to accomodate the physical limitations that our choice of a large beam width have imposed on the standard electron microscope column components.
